\selectlanguage{english}
\begin{abstract}
The Millikan experiment is proposed to determine the charge of the electron.
To achieve this, the falling velocity of an oil drop is measured under the
influence of gravity, buoyant force, and friction. Subsequently, a potential
difference is applied between plates, causing the drop to rise, and this ascent
velocity is measured.
The software \emph{Tracker} was used in this experiment to determine these
velocities.
Once the velocities are measured, an analysis of the involved forces is
performed to calculate the radius and charge of each drop.
A total of 20 drops were recorded, and using a code in \emph{Julia},
the greatest common divisor of the obtained charges was determined.
Finally, the charge of the electron was estimated to be approximately
\( e^{-} \approx \qty{1.50e-19}{C} \).
\end{abstract}

\begin{IEEEkeywords}
Millikan Experiment, Elementary Charge, Quantization.
\end{IEEEkeywords}

\selectlanguage{spanish}
\begin{abstract}
Se propone realizar el experimento de Millikan para determinar la carga del
electrón.
Para ello, se mide la velocidad de caída de una gota de aceite bajo la
influencia de la gravedad, la fuerza de empuje y la fricción.
Posteriormente, se aplica una diferencia de potencial entre placas, lo que
provoca una velocidad de ascenso de la gota, la cual se mide.
En esta práctica se utilizó el software \emph{Tracker} para determinar
dichas velocidades.
Una vez medidas las velocidades, se realiza un análisis de las fuerzas
involucradas para calcular el radio y la carga de cada gota.
Se registraron un total de 20 gotas, y mediante un código en \emph{Julia} se
determinó el mínimo común divisor de las cargas obtenidas.
Finalmente, se estimó que la carga del electrón es aproximadamente
\( e^{-} \approx \qty{1.50e-19}{C} \).
\end{abstract}

\begin{IEEEkeywords}
Experimento de Millikan; Carga elemental; Cuantización.
\end{IEEEkeywords}
